Concurrent Programming in Harmony

### 2021-01-19 book/paper.tex
Latest

\begin{figure}
\begin{code}
\begin{verbatim}
#states = 53 diameter = 5
==== Safety violation ====
T0: __init__() [0-4,31-46] 46 { count: 0, done[0]: False, done[1]: False }
T1: incrementer(0) [ 5- 8]  9 { count: 0, done[0]: False, done[1]: False }
T2: incrementer(1) [ 5-15] 15 { count: 1, done[0]: False, done[1]: True  }
T1: incrementer(0) [ 9-15] 15 { count: 1, done[0]: True,  done[1]: True  }
T3: main()         [17-27] 27 { count: 1, done[0]: True,  done[1]: True  }
>>> Harmony Assertion (file=code/Up.hny, line=10) failed: 1
Open file:///Users/rvr/github/harmony/harmony.html for more information
\end{verbatim}
\end{code}
\caption{The text output of running Harmony on \autoref{fig:inc}.}
\label{fig:incoutput}
\end{figure}

>>>>

\begin{figure}
\begin{code}
\begin{verbatim}
#states 32
Safety Violation
T0: __init__() [0-5,32-40] { count: 0, done: [ False, False ] }
T1: incrementer(0) [6 - 9] { count: 0, done: [ False, False ] }
T2: incrementer(1) [6 -18] { count: 1, done: [ False, True  ] }
T1: incrementer(0) [10-28] { count: 1, done: [ True,  True  ] }
Harmony assertion failed: 1
open file:///Users/rvr/github/harmony/harmony.html for more information
\end{verbatim}
\end{code}
\caption{The text output of running Harmony on \autoref{fig:inc}.}
\label{fig:incoutput}
\end{figure}
